---
title: "Class11"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The PDB Database

What percentage of structures solved by X-ray and electron microscopy? Also can
you determine what proportion of structures are protein?

```{r}
prop <- read.csv("Data Export Summary.csv", row.names = 1)
props_total <- prop$Total/sum(prop$Total)*100
names(props_total) <- rownames(prop)
props_total
```
Also can you determine what proportion of structures are protein?
```{r}
round(sum(prop$Proteins)/sum(prop$Total)*100, 1)
```


What if our data comes in another format? install.packages("datapasta"). Product isn't shown.
```{r}
tmp <- data.frame(stringsAsFactors=FALSE, row.names = 1,
   Experimental.Method = c("X-Ray", "NMR", "Electron Microscopy", "Other",
                           "Multi Method", "Total"),
              Proteins = c(124770, 10988, 2057, 250, 127, 138192),
         Nucleic.Acids = c(1993, 1273, 31, 4, 5, 3306),
    ProteinNA.Complex = c(6451, 257, 723, 6, 2, 7439),
                 Other = c(10, 8, 0, 13, 1, 32),
                 Total = c(133224, 12526, 2811, 273, 135, 148969)
)


```
## Section 3. Bio3D

Let's access our PDB file.

```{r}
pdb <- read.pdb("1hsg")
pdb
```

```{r}
view(pdb, "overview", col="sse")
```

Extract the protein-only portion of this PDB structure and write it out to a new PDB file.


To select the indices for all C-alpha atoms we can use the following command:
```{r}
ca.inds <- atom.select(pdb, "calpha")
ca.inds
prot.inds <- atom.select(pdb, "protein")
prot.inds
```
This produces the atom and xyz components and these numeric vectors can be used as indices to access the corresponding atom and xyz components of the input PDV structure obejct.
To get the first few atoms..:
```{r}
head( pdb$atom[ca.inds$atom, ] )
```
And to get the xyz coordinates...:
```{r}
head( pdb$xyz[, ca.inds$xyz] )
```
The In addition to the common selection strings (such as ‘calpha’ ‘cbeta’ ‘backbone’ ‘protein’ ‘notprotein’ ‘ligand’ ‘water’ ‘notwater’ ‘h’ and ‘noh’) various individual atom properties can be used for selection.
Extract the ligand (i.e. drug) and write out to a seperate file.
```{r}
# Select chain A
a.inds <- atom.select(pdb, chain="A")
# Select C-alphas of chain A
ca.inds <- atom.select(pdb, "calpha", chain="A")
# We can combine multiple selection criteria to return their intersection
cab.inds <- atom.select(pdb, elety=c("CA","CB"), chain="A",
resno=10:20)
inds <- atom.select(pdb, "ligand")
inds
```
```{r}
inds$atom
pdb$atom[inds$atom,]
```

```{r}
ligand.pdb <- trim.pdb(pdb,inds)
ligand.pdb
protein.pdb <- trim.pdb(pdb,prot.inds)
protein.pdb
```
```{r}
view(ligand.pdb)
```

```{r}
write.pdb(ligand.pdb, file = "ligand.pdb")
write.pdb(protein.pdb, file = "protein.pdb")
```

```{r}
pdb <- read.pdb("1HEL")

# Normal Mode Anlaysis
modes <- nma(pdb)
plot(modes)
```

```{r}
m7 <- mktrj(modes,mode=7,file="mode_7.pdb")
view(m7, col=vec2color( rmsf(m7) ))
```

