---
title: "Class09Project"
author: "Asha Goodman"
date: "2/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
 
```{r}
fna.data <- "WisconsinCancer.csv"
wisc.df <- read.csv(fna.data)
```

Always double check your data...
```{r}
head(wisc.df)
```
Looks like there is a funny last column :x:. Lets check how many samples (i.e. patients) and features (i.e. cols) are in this data
We want to find out how many patients, nrows tells us how many subjects..

```{r}
#number of patients
nrow(wisc.df)

# number of patients
ncol(wisc.df)
 
# To get both, use dim
dim(wisc.df)

# Want to get rid of patient ID (may want it in the future but for now we don't), and funny column, so take col 3 - 32
wisc.data <- wisc.df[,3:32]
head(wisc.data)
```
Add patient ID as row names of our data.
```{r}
# This lists the row names
rownames(wisc.data)

# But we want to tie the patient ids
rownames(wisc.data) <- wisc.df$id
head(wisc.data)
```
We want to find out how many cancer and noncancer data in this set? Table function will produce qauntification of the diagnoses.
```{r}
table(wisc.df$diagnosis)


```
How many of our columns include mean values? We would search column names and the grep function which tells us where in the vector our pattern is.
```{r}
# colnames(wisc.data)
grep("mean", colnames(wisc.data))
```
But how do we quantify these values?
```{r}
length(grep("mean", colnames(wisc.data)))
```
Also...
```{r}
inds <- grep("mean", colnames(wisc.data))
colnames(wisc.data)[inds]
# Finally, setup a separate new vector called diagnosis to be 1 if a diagnosis is malignant ("M") and 0 otherwise. Note that R coerces TRUE to 1 and FALSE to 0.

# Create diagnosis vector by completing the missing code
diagnosis <- as.numeric(wisc.df$diagnosis == "M")
diagnosis
```
## Now it's time to do PCA!

Scaling apply(x, #, pattern), x is your data, # = 1 would be rows, 2 is columns, pattern is mean, sd etc. And what it would give us is many sig figs, so rounding to '2' values is better.

When using the prcomp function, the scale function by default is false.
```{r}
round( apply(wisc.data,2,sd), 2)
wisc.pr  <- prcomp(wisc.data, scale = TRUE)
summary(wisc.pr)
```
```{r}
attributes(wisc.pr)
```
```{r}
# This is a basic first plot
biplot(wisc.pr)

# This is going to be our more traditional pca plot
plot( wisc.pr$x[,1], wisc.pr$x[,2] , col = wisc.df$diagnosis, 
     xlab = "PC1", ylab = "PC2")

```

```{r}
variance <- wisc.pr$sdev^2
pve <- round((variance/sum(variance))*100,2)
plot(pve, type="o")
pr.var <- pve
head(pr.var)
```
To get data-driven axeses, see below.
```{r}
barplot(pve, ylab = "Percent of Variance Explained",
     names.arg=paste0("PC",1:length(pve)), las=2, axes = FALSE)
axis(2, at=pve, labels=round(pve,2)*100 )
```
## CLustering in Principal COmponent Space

For hclust we need a distance matrix and wee get this from our PCA results (i.e. wisc.pr$x)
```{r}
d <- dist(wisc.pr$x[,1:2])
hc <- hclust(d, method="ward.D2")
plot(hc)
```
Now we want three maor groups.
```{r}
# cutree(hc, k=3) is our command
grps3 <- cutree(hc, k=3)
table(grps3)

```
Let's color our PCA plot by cluster.

```{r}
plot( wisc.pr$x[,1], wisc.pr$x[,2] , col = grps3, 
     xlab = "PC1", ylab = "PC2")
```
Cross tabulation
```{r}
# table(grps3)
table(grps3, diagnosis)
```

```{r}
plot( wisc.pr$x[,1:2], col = grps3, 
     xlab = "PC1", ylab = "PC2")
```
```{r}
plot(wisc.pr$x[,1:2], col=diagnosis+1)
```
Prediction function will take our PCA model from before and new cancer cell data and project that data onto our PCA space. So let's bring in the new data.
```{r}
url <- "new_samples.csv"
new <- read.csv(url)
npc <- predict (wisc.pr, newdata=new)
```
And now let's plot the new data onto our graphs.
```{r}
plot(wisc.pr$x[,1:2], col=wisc.df$diagnosis)
points(npc[,1], npc[,2], col=c("green","blue"), pch=16, cex=3)
```


