---
title: "Class 12 Drug Discovery"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## CLean up our protein target structure

First we download a target strcutre from the main PDV database. We will pick PDB ID "1hsg".

```{r}
library(bio3d)
hsgPDB <- get.pdb("1HSG")
hsgPDB
hiv <- read.pdb(hsgPDB)
hiv
```
Then we want to extract the protein only segment of this PDB entry and write out a new PDB format file. We will aslo do the same for the bound ligand.
```{r}
proteinhiv <- trim.pdb(hiv, "protein")
ligandhiv <- trim.pdb(hiv, "ligand")

prot.filename <- paste(hsgPDB,"_protein.pdb", sep="")
write.pdb(proteinhiv, file=prot.filename)
#write.pdb(proteinhiv, file = "1hsg_protein.pdb")
#write.pdb(ligandhiv, file = "1hsg_ligand.pdb")
prot.filename

lig.filename <- paste(hsgPDB, "_ligand.pdb", sep="")
write.pdb(ligandhiv, file=lig.filename)
lig.filename

```


```{r}
#Normal mode analysis
modes <- nma(hiv)
plot(modes)
```
## Convert our docking results for viewin in VMD

```{r}
res <- read.pdb("all.pdbqt", multi=TRUE)
write.pdb(res, "results.pdb")
```

# What is the RMSD to the MK1 compound from the crystal structur?
```{r}
# res <- read.pdb("all.pdbqt", multi=TRUE)
ori <- read.pdb("ligand.pdbqt")
rmsd(ori, res)
```


