---
title: "Class 6 R Functions"
author: "Asha Goodman"
date: "1/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## File reading (again!)

Here we try to use **read.table()** and friends to input some example data into R.

Lets insert a code chunk.
```{r}
read.csv("https://bioboot.github.io/bggn213_S18/class-material/test1.txt")
```

```{r}
file2  <- "https://bioboot.github.io/bggn213_S18/class-material/test2.txt"
read.csv(file2, sep = "$")
```

```{r}
file3 <- "https://bioboot.github.io/bggn213_S18/class-material/test3.txt"
data3 <- read.table(file3)
data3
```

## R Functions

My first function
```{r}
add <- function(x, y=1) {
  #sum x and y
  x + y
}
```
Lets use the **add** function
```{r}
add(1,50)
```

This is a purposeful error:
add(x=1,y="b")

# Our Second Function
```{r}
rescale <- function(x) {
 rng <-range(x)
 (x - rng[1]) / (rng[2] - rng[1])
}
```

How would our function work here?
```{r}
rescale( c(1,2,NA,3,10) )
```
Well we have to change our function to omit "NA"s
rescale <- function(x) {
 rng <-range(x, **na.rm=true**)
 (x - rng[1]) / (rng[2] - rng[1])
}
```{r}
rescale <- function(x) {
 rng <-range(x, na.rm=T)
 (x - rng[1]) / (rng[2] - rng[1])
}
rescale( c(1,2,NA,3,10))
```

Or here?

rescale( c(1,10,”string”) )


rescale <- function(x) {
 rng <-range(...)
 (x - rng[1]) / (rng[2] - rng[1])
 rescale( c(1,10,”string”) )
# Print Function
```{r}
rescale3 <- function(x, na.rm=TRUE, plot=FALSE)
{
 if(na.rm) {
 rng <-range(x, na.rm=na.rm)
 } else {
 rng <-range(x)
 }
 print("Hello")
 answer <- (x - rng[1]) / (rng[2] - rng[1])

 print("is it me you are looking for?")
 if(plot) {
 plot(answer, typ="b", lwd=4)
 }
 print("I can see it in ...")
 return(answer)
}
rescale3(1:10)
```

## Using the Bio3d package

Have to go to the library to get the package before you use it every time.
```{r}
library(bio3d)
```

What's in this pdb?
```{r}
pdb <- read.pdb("1hbs")
pdb
```
# Can you improve this analysis code?
```{r}
library(bio3d)
Test <- read.pdb("4AKE") # kinase with drug
Control <- read.pdb("1AKE") # kinase no drug
Test2 <- read.pdb("1E4Y") # kinase with drug
Test.chainA <- trim.pdb(Test, chain="A", elety="CA")
Control.chainA <- trim.pdb(Control, chain="A", elety="CA")
Test2.chainA <- trim.pdb(Test2, chain="A", elety="CA")
Test.b <- Test.chainA$atom$b
Control.b <- Control.chainA$atom$b
Test2.b <- Test2.chainA$atom$b
plotb3(Test.b, sse=Test.chainA, typ="l", ylab="Bfactor")
plotb3(Control.b, sse=Control.chainA, typ="l", ylab="Bfactor")
plotb3(Test2.b, sse=Test2.chainA, typ="l", ylab="Bfactor")
```

# Answered simply, yes we can. Note we have now made a new function that encompasses the previous functions that **R**eads **a**nd **P**lots a **pdb for me** or "rap_pdb_forme". This function takes advantage of vectors and their isolation in the function. For example, although we have assigned "x2" as a read.pdb file, that vector does not exist outside of this function. You may use this function as though it is a read.pdb function, and simply insert the name of your protein of interest e.g. "4AKE".

# This function reads the pdb file, identifies the "A" chains and the atom type (elety) and draws a standard scatter plot with lines. The plot has residues as the x-axis and a y-axis labelled "Bfactor".

```{r}
library(bio3d)
rap_pdb_forme <- function(x){
  x2 <- read.pdb(x)
  x3.b <- trim.pdb(x2, chain="A", elety = "CA")
  x4.chainA <- x3.b$atom$b
  plotb3(x4.chainA, sse = x4.chainA, typ="l", ylab="Bfactor")
}
rap_pdb_forme("4AKE")
rap_pdb_forme("1AKE")
rap_pdb_forme("1E4Y")
```


