---
title: "Code Generalization"
author: "Asha Goodman"
date: "1/29/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Can you improve this analysis code?
```{r}
library(bio3d)
Test <- read.pdb("4AKE") 
Control <- read.pdb("1AKE") 
Test2 <- read.pdb("1E4Y") 
Test.chainA <- trim.pdb(Test, chain="A", elety="CA")
Control.chainA <- trim.pdb(Control, chain="A", elety="CA")
Test2.chainA <- trim.pdb(Test2, chain="A", elety="CA")
Test.b <- Test.chainA$atom$b
Control.b <- Control.chainA$atom$b
Test2.b <- Test2.chainA$atom$b
plotb3(Test.b, sse=Test.chainA, typ="l", ylab="Bfactor")
plotb3(Control.b, sse=Control.chainA, typ="l", ylab="Bfactor")
plotb3(Test2.b, sse=Test2.chainA, typ="l", ylab="Bfactor")
```

Answered simply, yes we can. Note we have now made a new function that encompasses the previous functions that **R**eads, trims, **a**nd **P**lots a **pdb for me** or "rap_pdb_forme". This function takes advantage of vectors and their isolation in the function. For example, although we have assigned "x2" as a read.pdb file, that vector does not exist outside of this function. You may use this function as though it is a read.pdb function, and simply insert the name of your protein of interest e.g. "4AKE".

This function reads the pdb file, identifies the "A" chains and the atom type (elety) and draws a standard scatter plot with lines. The plot has residues as the x-axis and a y-axis labelled "Bfactor".

```{r}
library(bio3d)
rap_pdb_forme <- function(x){
  for (i in x){
  x2 <- read.pdb(i)
  if (i == numeric){
    stop("Input x is not a pdb file name")
  }
  x3.b <- trim.pdb(x2, chain="A", elety = "CA")
  x4.chainA <- x3.b$atom$b
  plotb3(x4.chainA, sse = x3.b, typ="l", ylab="Bfactor")
  }
}
rap_pdb_forme(c("4AKE", "1AKE", "1E4Y"))
```
