---
title: "Class 7 Functions and Packages"
author: "Asha Goodman"
date: "1/30/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Functions revisited

Load (i.e. **source**) our rescae() function from the last day.

```{r}
source("http://tinyurl.com/rescale-R")
```

Test this function

> rescale(c (1:5, "string"))

If you were to run this function, "Error in x - rng[1] : non-numeric argument to binary operator" would appear, saying this error happens in the function.

We want to make this function more robust to these types of errors.
The warning() and stop() functions are helpful. Both pring a user defined messsage. Warning() will keep going on however, while stop() keeps going. But it's better to fail early and loudly.

example:

>  if(!is.numeric(x) )
>  stop(("input"" x "should be numeric", call.FALSE))

This bit of code can be put into rescale, thus rescale 2.

> rescale2( c(1:5, "string") )

gives us Error: Input x should be numeric Execution halted.

> x <- c(NA, NA, NA)
> y1 <- c(1, NA, NA)
> y2 <- c( 1, NA, NA, NA)
> y3 <- c(1, NA, NA, NA, NA)

what will this return?

> both_na(x, y2) 

```{r}
x <- c(NA, NA, NA)
y1 <- c(1, NA, NA)
y2 <- c( 1, NA, NA, NA)
y3 <- c(1, NA, NA, NA, NA)

both_na(x, y2)
```

```{r}
both_na(x, y3)
```

```{r}
both_na2(x, y2)
```
```{r}
# Lets make an example
x2 <- c(NA, 2, NA, 4, 5)
y <- c(5, 4, NA, 2, NA)
both_na3(x2, y)
```





